An assessment of photometric redshift PDF performance in the context of LSST

### 2018-11-16 paper/main.tex
adress appendix comments, add refs for code packages

The authors would like to thank their LSST-DESC publication review committee.

@@

>>>>

The authors would like to thank their LSST-DESC publication review committee for comments that improved the paper draft.

@@

In addition to packages cited in the text, analyses performed in this paper used the following software packages: \textsc{Numpy} and \textsc{Scipy} \citep{numpyscipy}, \textsc{Matplotlib} \citep{matplotlib}, \textsc{Seaborn} \citep{seaborn},

### 2018-11-16 paper/tex/appendix.tex
finished adding re-run of GPz with proper training
adress appendix comments, add refs for code packages

\section{Point Estimate Photometric Redshifts}
\label{sec:pointmetrics}
While we do not recommend the use of single point estimates of redshift for most science applications, plots of the point estimates can be a useful qualitative diagnostic of photo-z code performance, i.~e.~examining point photo-$z$ vs.~spec-$z$ plots visually can give a quick impression of some common trends in different codes.  Computing point estimate statistics may also be useful for more direct comparisons with previous photo-z evaluations.  If a point-estimate is preferred for a specific science case, it is fairly simple to compute the mean, mode, or some other simple estimator from each $p(z)$, so these point estimates can be easily derived from the stored $p(z)$.

@@

Finally, we note that all eleven codes are at or near the goals for point-estimates as outlined in the LSST Science Requirements Document\footnote{available at: \url{http://ls.st/srd}} and \citet{Graham:17}.  This is to be expected, given that the requirements were designed such that a point estimate photo-z would meet these requirements for perfect training data to a depth of $i<25$.  But, it is still an encouraging sign, given an updated mock galaxy simulation and the expanded set of photo-$z$ codes tested.
%\red{maybe say consistent with expectations, and a reference to Melissa's paper in here?  What else to say about nearly meeting point goals?}

@@

\begin{table*}
\begin{center}
\caption{Point estimate statistics}\label{tab:pointestimates}
\begin{tabular}{lcccccc}
\hline
\hline
                 &            & $Z_{PEAK}$  &          &  & $Z_{WEIGHT}$          &\\
\hline
Photo-z Code       & $\frac{\sigma_{IQR}}{(1+z)}$ & median  & \multicolumn{1}{|p{0.75cm}|}{\centering outlier \\fraction} & $\frac{\sigma_{IQR}}{(1+z)}$ & median & \multicolumn{1}{|p{0.75cm}|}{\centering outlier \\fraction}\\
\hline
\textsc{ANNz2}     & 0.0270  &  0.00063  & 0.044      & 0.0244  &  0.000307  & 0.047  \\
\textsc{BPZ}       & 0.0215  & -0.00175  & 0.035      & 0.0215  & -0.002005  & 0.032 \\
\textsc{Delight}   & 0.0212  & -0.00185  & 0.038      & 0.0216  & -0.002158  & 0.038 \\
\textsc{EAZY}      & 0.0225  & -0.00218  & 0.034      & 0.0226  & -0.003765  & 0.029 \\
\textsc{FlexZBoost}& 0.0154  & -0.00027  & 0.020      & 0.0148  & -0.000211  & 0.017 \\
\textsc{GPz}       & 0.0202  & -0.00091  & 0.036      & 0.0201  & -0.000950  & 0.037 \\
\textsc{LePhare}   & 0.0236  & -0.00161  & 0.058      & 0.0239  & -0.002007  & 0.056 \\
\textsc{METAPhoR}  & 0.0264  &  0.00000  & 0.037      & 0.0262  &  0.001333  & 0.048 \\
\textsc{CMNN}        & 0.0184  & -0.00132  & 0.035      & 0.0170  & -0.001049  & 0.034 \\
\textsc{Skynet}    & 0.0219  & -0.00167  & 0.036      & 0.0218  &  0.000174  & 0.037 \\
\textsc{TPZ}       & 0.0161  &  0.00309  & 0.033      & 0.0166  &  0.003048  & 0.031 \\
\hline
\trainz	   & 0.1808  &  -0.2086  & 0.000	  & 0.2335  & 0.022135  & 0.000\\
\end{tabular}
\end{center}
\end{table*}

>>>>

\section{Point Estimate Photometric Redshifts}
\label{sec:pointmetrics}
While we assume that all science analysis will use full PDF information and do not recommend the use of single point estimates of redshift for most science applications, we include a brief evaulation as an Appendix.  Plots of the point estimates can be a useful qualitative diagnostic of photo-z code performance, i.~e.~examining point photo-$z$ vs.~spec-$z$ plots visually can give a quick impression of some common trends in different codes.  Computing point estimate statistics may also be useful for more direct historical comparisons from older photo-z evaluations.  If a point-estimate is preferred for a specific science case, it is fairly simple to compute the mean, mode, or some other simple estimator from each $p(z)$, so these point estimates can be easily derived from the stored $p(z)$.

@@

Finally, we note that all twelve codes perform at or near the goals for point-estimates as outlined in the LSST Science Requirements Document\footnote{available at: \url{http://ls.st/srd}} and \citet{Graham:17}.  This is to be expected, given that the requirements were designed such that a point estimate photo-z would meet these requirements for perfect training data to a depth of $i<25$.  But, it is still an encouraging sign, given an updated mock galaxy simulation and the expanded set of photo-$z$ codes tested.
%\red{maybe say consistent with expectations, and a reference to Melissa's paper in here?  What else to say about nearly meeting point goals?}

@@

\begin{table*}
\begin{center}
\caption{Point estimate statistics}\label{tab:pointestimates}
\begin{tabular}{lcccccc}
\hline
\hline
                 &            & $Z_{PEAK}$  &          &  & $Z_{WEIGHT}$          &\\
\hline
Photo-z Code       & $\frac{\sigma_{IQR}}{(1+z)}$ & median  & \multicolumn{1}{|p{0.75cm}|}{\centering outlier \\fraction} & $\frac{\sigma_{IQR}}{(1+z)}$ & median & \multicolumn{1}{|p{0.75cm}|}{\centering outlier \\fraction}\\
\hline
\textsc{ANNz2}     & 0.0270  &  0.00063  & 0.044      & 0.0244  &  0.000307  & 0.047  \\
\textsc{BPZ}       & 0.0215  & -0.00175  & 0.035      & 0.0215  & -0.002005  & 0.032 \\
\textsc{Delight}   & 0.0212  & -0.00185  & 0.038      & 0.0216  & -0.002158  & 0.038 \\
\textsc{EAZY}      & 0.0225  & -0.00218  & 0.034      & 0.0226  & -0.003765  & 0.029 \\
\textsc{FlexZBoost}& 0.0154  & -0.00027  & 0.020      & 0.0148  & -0.000211  & 0.017 \\
\textsc{GPz}       & 0.0197  & -0.00000  & 0.052      & 0.0195  &  0.000113  & 0.051 \\
\textsc{LePhare}   & 0.0236  & -0.00161  & 0.058      & 0.0239  & -0.002007  & 0.056 \\
\textsc{METAPhoR}  & 0.0264  &  0.00000  & 0.037      & 0.0262  &  0.001333  & 0.048 \\
\textsc{CMNN}        & 0.0184  & -0.00132  & 0.035      & 0.0170  & -0.001049  & 0.034 \\
\textsc{Skynet}    & 0.0219  & -0.00167  & 0.036      & 0.0218  &  0.000174  & 0.037 \\
\textsc{TPZ}       & 0.0161  &  0.00309  & 0.033      & 0.0166  &  0.003048  & 0.031 \\
\hline
\trainz	   & 0.1808  &  -0.2086  & 0.000	  & 0.2335  & 0.022135  & 0.000\\
\end{tabular}
\end{center}
\end{table*}
